A Review of Lossless Data Compression Methods

### 2018-11-17 paper.tex
Add internal references.

\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsthm, amsfonts}
\usepackage{tikz}
\usepackage[pdfusetitle]{hyperref}
\usepackage{apacite}

@@

\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}{Proposition}
\newtheorem{defn}{Definition}[section]

\title{A Review of Lossless Data Compression Methods}
\author{Blargh}

@@

\begin{thm}
  For any given data compression scheme, there exists at least one
  arbitrary input data whose ``compressed'' form is not strictly
  shorter than it. That is to say, there is no compression scheme
  which can compress every potential input.
\end{thm}

@@

\begin{thm}
  The average word length of an optimal prefix code for a given source
  is greater than or equal to the entropy of that source.
\end{thm}

@@

The basic method introduced in Lempel and Ziv's original paper is
vulnerable to some significant drawbacks. Since each individual byte
in the input can take up at most three bytes in the output, it is
possible that some pathological input data can have a compressed form
which is substantially larger, especially if the sliding window is
small. As such, this suggests a good jumping-off point for creating
improvements upon the original algorithm.

>>>>

\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsthm, amsfonts}
\usepackage{thmtools}
\usepackage{tikz}
\usepackage[pdfusetitle]{hyperref}
\usepackage{cleveref}
\usepackage{apacite}

@@

\declaretheorem[numberwithin=section]{Theorem}

\title{A Review of Lossless Data Compression Methods}
\author{Citoyen}

@@

\begin{Theorem}
  \label{imperfect-compression}
  For any given data compression scheme, there exists at least one
  arbitrary input data whose ``compressed'' form is not strictly
  shorter than it. That is to say, there is no compression scheme
  which can compress every potential input.
\end{Theorem}

@@

\begin{Theorem}
  \label{snct}
  The average word length of an optimal prefix code for a given source
  is greater than or equal to the entropy of that source.
\end{Theorem}

@@

The basic method introduced in Lempel and Ziv's original paper is
vulnerable to some significant drawbacks. For instance, since each
individual byte in the input can take up at most three bytes in the
output, it is possible that some pathological input data can have a
compressed form which is substantially larger, especially if the
sliding window is small. (Clearly, a highly entropic input is much
more likely to have fewer recurring prefixes within any given sliding
window, which is consistent with our result from
\Cref{imperfect-compression}) As such, this suggests a good jumping-off
point for creating improvements upon the original algorithm.
